---
title: "STA 141  APPENDIX"
author: "Yesuunee" 
output:
  html_document: default
  pdf_document: default
  word_document: default
---
author: "Yesuunee"

```{r}

library(readr)
student_por <- read_csv('/Users/Sia/Documents/UC Davis Quarters/Spring 2020/STA 141A/student-por.csv')
d2=data.frame(student_por)

```


Does student alcohol consumption affect grades, number of past class failures, and absences?


#Normality test 
```{r}

linmodel= lm(d2$Dalc~d2$famsize+d2$Pstatus+ d2$famrel,data=d2)
plot(linmodel)
```

#Model Selection 
```{r}
library(MASS)

#Family background selection 

# Fit the full model Weekday Alcohol consumption
full.modelD <- lm(d2$Dalc ~ d2$address + d2$famsize+ d2$Pstatus+ d2$Medu+ d2$Fedu+ d2$Fedu+ d2$Mjob+ d2$Fjob+ d2$famsup++ d2$famrel , data = d2)
#Fit the null model 
null.modelD <- lm(d2$Dalc~1, data=d2)
# Stepwise regression model
step.modelD <- stepAIC(full.modelD, direction = "both", 
                      trace = FALSE)

ForwardAICD=step(null.modelD, scope= list(lower=null.modelD, upper=full.modelD), direction= "forward" ) 
BAckwardAICD=step(full.modelD, scope=list(lower=null.modelD, upper = full.modelD), direction = "backward")

summary(ForwardAICD)
summary(BAckwardAICD)



```


###Corrolation Between alchohol consumtion(weekday & weekend) and grades.  

###Dalc 
```{r}
grade.x <-cor.test(d2$G3, d2$Dalc,  method = "spearman")
grade.x

```
A weak downhill relationship 
###FIX 
```{r}
bx1=boxplot(d2$G3 ~ d2$Dalc, ylab = "Grade", xlab = " Weekday Alcohol Consumption in Language class")

```
Those who consume amount of alchohol 2 has lower grade. Those who consume 1 has significantly better score than those who consume alcohol around 3,4 and 5. 

###Corrolation Between alchohol consumption(weekday & weekend) and classs failures. 

```{r}
fail.x <-cor.test(d2$failures,  d2$Dalc,  method = "spearman")
fail.x
```
There are no significant difference in class failures. 


```{r}
bx3=boxplot(d2$failures ~ d2$Dalc, ylab = "Number of Class Failures", xlab = "Weekday Alcohol Consumption in Portuguese class")

```


###Corrolation Between alchohol consumption(weekday & weekend) and absences. 


```{r}
abs.x <-cor.test(d2$absences,  d2$Dalc,  method = "spearman")
abs.x
```


```{r}
bx5=boxplot(d2$absences ~ d2$Dalc,  ylab = "Number of Absences", xlab = "Weekday Alcohol Consumption in Portuguese class")
```

The absence is high for those whose alchohol consumptions are 3, 5. (4??)
For math class the absence increases as the alcohol consumption increase. 


###Walc 

###Corrolation Between alchohol consumption(weekday & weekend) and grades. 
```{r}
grade.wx <-cor.test(d2$G3, d2$Walc,  method = "spearman")
grade.wx

```
A weak downhill relationship 

```{r}
bx7=boxplot(d2$G3 ~ d2$Walc, ylab = "Grade", xlab = "Weekend Alcohol Consumption in Language class")
```
Those who consume amount of alchohol 2 has lower grade. Those who consume 1 has significantly better score than those who consume alcohol around 3,4 and 5. 

###Corrolation Between alchohol consumption(weekday & weekend) and classs failures. 

```{r}
fail.wx <-cor.test(d2$failures,  d2$Walc,  method = "spearman")
fail.wx
```


```{r}
bx9=boxplot(d2$failures ~ d2$Walc, ylab = "Number of Class Failures", xlab = "Weekend Alcohol Consumption in Language class")
```


###Corrolation Between alchohol consumption(weekday & weekend) and absences. 


```{r}
abs.wx <-cor.test(d2$absences,  d2$Walc,  method = "spearman")
abs.wx
```


```{r}
bx11=boxplot(d2$absences ~ d2$Walc, ylab = "Number of Class Absences", xlab = "Weekend Alcohol Consumption in Language class")
```


### R Appendix
```{r, ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE}
```




